---
title: "Exploring Meat toy model"
output: html_notebook
---
```{r, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(reshape2)
library(tidyr)
library(magrittr)
library(plyr)
library(dplyr)
library(ggplot2)
library(magrittr)
```

 
# NETLOGO TOY MODEL

__TODO__

- changer le script scala pour passer des parametres directement depuis le notebook !
- prendre en sorte le fait qu'on a 3 données par pas de temps dans le graphique 

## Producing csv outputs

You could produce csv outputs of Netlogo MeatModel using Netlogo interface by opening the `./toy/PicSaintLoup/MeatModel-V5` model, running some experiments, and when you're donne, clic on the button save-csv. 

If you have `sbt` build engine installed on your computer you could also run this headless script by running this chunk directly from R/RStudio. 

`./toy/PicSaintLoup/MeatModel-V5` folder. 
```{bash, include=FALSE}
cd ../toy/PicSaintLoup/
sbt run
```

## Producing explorations

```{r, message=FALSE, warning=FALSE, include=FALSE}
apparie <- read_csv("../toy/PicSaintLoup/models/outputs/apparie.csv",col_names = FALSE) 
voisins <- read_csv("../toy/PicSaintLoup/models/outputs/voisins.csv",col_names = FALSE) 
opinion <- read_csv("../toy/PicSaintLoup/models/outputs/opinion.csv",col_names = FALSE) 

apparie$X5 <-  gsub("\\[|\\]", "", apparie$X5)
voisins$X5 <- gsub("\\[|\\]", "", voisins$X5)
opinion$X5 <- gsub("\\[|\\]", "", opinion$X5)

l <- strsplit(first(apparie$X5)," " )
sizeSeq <- seq(lengths(l))

dfApparie <- with(apparie, cbind(X1,X2,X3,X4, colsplit(apparie$X5, " ", names = sizeSeq) ))

dfVoisins <- with(voisins, cbind(X1,X2,X3,X4, colsplit(voisins$X5, " ", names = sizeSeq) ))

dfOpinion <- with(opinion, cbind(X1,X2,X3,X4, colsplit(opinion$X5, " ", names = sizeSeq) ))

names(dfApparie)[1] <- paste("who")
names(dfApparie)[2] <- paste("age")
names(dfApparie)[3] <- paste("sex")
names(dfApparie)[4] <- paste("edu")

names(dfVoisins)[1] <- paste("who")
names(dfVoisins)[2] <- paste("age")
names(dfVoisins)[3] <- paste("sex")
names(dfVoisins)[4] <- paste("edu")

names(dfOpinion)[1] <- paste("who")
names(dfOpinion)[2] <- paste("age")
names(dfOpinion)[3] <- paste("sex")
names(dfOpinion)[4] <- paste("edu")

gDfApparie <- gather(data = dfApparie, key = time, value= nb,  c(5:34))
gDfOpinion <- gather(dfOpinion, time, ValueOpinion, c(5:34))
gDfVoisins <- gather(dfVoisins, time, nbVoisins, c(5:34)) 

gdfFinal <- join(gDfApparie, gDfOpinion, by=c("who","age","sex","edu","time"), type="inner")
gdfFinal <- join(gdfFinal, gDfVoisins, by=c("who","age","sex","edu","time"), type="inner")
gdfFinal$time <- as.numeric(gdfFinal$time)
  
#gdFinalSubset <- gdfFinal[gdfFinal$time < 20.0,]

gdFinalByAge_valueOpinion <- gdfFinal %>% group_by(age,time) %>%
  summarise_each(funs(mean), ValueOpinion)

gdFinalBySex_valueOpinion <- gdfFinal %>% group_by(sex,time) %>%
  summarise_each(funs(mean), ValueOpinion)

gdFinalByEdu_valueOpinion <- gdfFinal %>% group_by(edu,time) %>%
  summarise_each(funs(mean), ValueOpinion)


gdFinalByAge_nbVoisin <- gdfFinal %>% group_by(age,time) %>%
  summarise_each(funs(mean), nbVoisins)

gdFinalBySex_nbVoisin <- gdfFinal %>% group_by(sex,time) %>%
  summarise_each(funs(mean), nbVoisins)

gdFinalByEdu_nbVoisin <- gdfFinal %>% group_by(edu,time) %>%
  summarise_each(funs(mean), nbVoisins)


gdFinalByAge_apparie <- gdfFinal %>% group_by(age,time) %>%
  summarise_each(funs(mean), nb)

gdFinalBySex_apparie <- gdfFinal %>% group_by(sex,time) %>%
  summarise_each(funs(mean), nb)

gdFinalByEdu_apparie <- gdfFinal %>% group_by(edu,time) %>%
  summarise_each(funs(mean), nb)
```

### TO LONG DATA AGE

```{r, warning=FALSE}
gdfFinalAge <- merge(gdFinalByAge_valueOpinion, gdFinalByAge_nbVoisin, by=c("age","time"), type="inner")
gdfFinalAge <- merge(gdfFinalAge, gdFinalByAge_apparie, by=c("age","time"), type="inner")

gDfToLongAge <- gather(gdfFinalAge, facteur, value , by=c(ValueOpinion,nb,nbVoisins))

p <- ggplot(data=gDfToLongAge, aes(x=time, y=value, group=age, fill=age, colour=as.character(age)))
p <- p + geom_line(size=1) + facet_grid(facteur ~ .) #show.legend = FALSE
p
```

### TO LONG DATA EDU

```{r, warning=FALSE}
gdfFinalEdu <- merge(gdFinalByEdu_valueOpinion, gdFinalByEdu_nbVoisin, by=c("edu", "time"), type="inner")
gdfFinalEdu <- merge(gdfFinalEdu, gdFinalByEdu_apparie, by=c("edu","time"), type="inner")

gDfToLongEdu <- gather(gdfFinalEdu, facteur, value , by=c(ValueOpinion,nb,nbVoisins))

p <- ggplot(data=gDfToLongEdu, aes(x=time, y=value, group=edu, fill=edu, colour=as.character(edu)))
p <- p + geom_line(size=1) + facet_grid(facteur ~ .) #show.legend = FALSE
p
```

### TO LONG DATA SEX

```{r, warning=FALSE}
gdfFinalSex <- merge(gdFinalBySex_valueOpinion, gdFinalBySex_nbVoisin, by=c("sex", "time"), type="inner")
gdfFinalSex <- merge(gdfFinalSex, gdFinalBySex_apparie, by=c("sex","time"), type="inner")

gDfToLongSex <- gather(gdfFinalSex, facteur, value , by=c(ValueOpinion,nb,nbVoisins))

p <- ggplot(data=gDfToLongSex, aes(x=time, y=value, group=sex, fill=sex, colour=as.character(sex)))
p <- p + geom_line(size=1) + facet_grid(facteur ~ .) #show.legend = FALSE
p
```

# FAT MODEL 

## Exploring scenarii

# random residential scenario 1

-----------------------------------------------------------------------------------------------------------
 maxProbaToSwitch    constraintsStrength         inertiaCoefficient         healthyDietReward         seed
-----------------    -------------------         ------------------         -----------------         ----
0.8                  0.05                         0.5                        0.4                       42
-----------------------------------------------------------------------------------------------------------


```{r, fig.width=10}
sortie_sc1 <- read_csv("../data/CIST2018/random_residential_scenario1/csv/categories.csv",col_names = TRUE, col_types= "nnnnnnnn")
sortie_sc1$propHealthy <- sortie_sc1$healthy / sortie_sc1$effective 
  
sortieLong_sc1 <- gather(sortie_sc1, facteur, valeur, by=c(propHealthy,avgOpinion) ) 

sortieLong_sc1 <- mutate(sortieLong_sc1, "ds" = gsub(" ", "", paste(paste("[",paste(sortieLong_sc1$day, sortieLong_sc1$slice)),"]")))

p <- ggplot(data=sortieLong_sc1, aes(x=ds, y=valeur, group=educ, fill=educ, colour=as.character(educ)))
p <- p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p <- p + geom_line(size=0.5) + facet_grid(facteur ~ sex ~ age) #show.legend = FALSE
p
```

# survey residential scenario 2

-----------------------------------------------------------------------------------------------------------
 maxProbaToSwitch    constraintsStrength         inertiaCoefficient         healthyDietReward         seed
-----------------    -------------------         ------------------         -----------------         ----
0.8                  0.05                         0.5                        0.4                       42
-----------------------------------------------------------------------------------------------------------



```{r, fig.width=10}
sortie_sc2 <- read_csv("../data/CIST2018/survey_residential_scenario2/csv/categories.csv",col_names = TRUE, col_types= "nnnnnnnn")
sortie_sc2$propHealthy <- sortie_sc2$healthy / sortie_sc2$effective 
  
sortieLong_sc2 <- gather(sortie_sc2, facteur, valeur, by=c(propHealthy,avgOpinion) ) 

sortieLong_sc2 <- mutate(sortieLong_sc2, "ds" = gsub(" ", "", paste(paste("[",paste(sortieLong_sc2$day, sortieLong_sc2$slice)),"]")))

p <- ggplot(data=sortieLong_sc2, aes(x=ds, y=valeur, group=educ, fill=educ, colour=as.character(educ)))
p <- p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p <- p + geom_line(size=0.5) + facet_grid(facteur ~ sex ~ age) #show.legend = FALSE
p
```

# random activity scenario 3

-----------------------------------------------------------------------------------------------------------
 maxProbaToSwitch    constraintsStrength         inertiaCoefficient         healthyDietReward         seed
-----------------    -------------------         ------------------         -----------------         ----
0.8                  0.5                         0.5                        0.4                       42
-----------------------------------------------------------------------------------------------------------

```{r, fig.width=10}
sortie_sc3 <- read_csv("../data/CIST2018/random_activity_scenario3/csv/categories.csv",col_names = TRUE, col_types= "nnnnnnnn")
sortie_sc3$propHealthy <- sortie_sc3$healthy / sortie_sc3$effective 
  
sortieLong_sc3 <- gather(sortie_sc3, facteur, valeur, by=c(propHealthy,avgOpinion) ) 

sortieLong_sc3 <- mutate(sortieLong_sc3, "ds" = gsub(" ", "", paste(paste("[",paste(sortieLong_sc3$day, sortieLong_sc3$slice)),"]")))

p <- ggplot(data=sortieLong_sc3, aes(x=ds, y=valeur, group=educ, fill=educ, colour=as.character(educ)))
p <- p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p <- p + geom_line(size=0.5) + facet_grid(facteur ~ sex ~ age) #show.legend = FALSE
p
```

# survey activity scenario 4

-----------------------------------------------------------------------------------------------------------
 maxProbaToSwitch    constraintsStrength         inertiaCoefficient         healthyDietReward         seed
-----------------    -------------------         ------------------         -----------------         ----
0.8                  0.05                        0.5                        0.4                       42
-----------------------------------------------------------------------------------------------------------

```{r, fig.width=10}
sortie_sc4 <- read_csv("../data/CIST2018/survey_activity_scenario4/csv/categories.csv",col_names = TRUE, col_types= "nnnnnnnn")
sortie_sc4$propHealthy <- sortie_sc4$healthy / sortie_sc4$effective 
  
sortieLong_sc4 <- gather(sortie_sc4, facteur, valeur, by=c(propHealthy,avgOpinion) ) 
sortieLong_sc4 <- mutate(sortieLong_sc4, "ds" = gsub(" ", "", paste(paste("[",paste(sortieLong_sc4$day, sortieLong_sc4$slice)),"]")))

p <- ggplot(data=sortieLong_sc4, aes(x=ds, y=valeur, group=educ, fill=educ, colour=as.character(educ)))
p <- p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p <- p + geom_line(size=0.5) + facet_grid(facteur ~ sex ~ age) #show.legend = FALSE
p
```



